Methods for Polyphonic Music Transcription

### 2013-12-11 paper/paper.tex
added stuff

\section{Introduction}

\subsection{Terminology}
Semitones are the smallest music interval in Western music. On a piano, semitones are the adjacent keys.

@@

Some have suggested adding additional bases to $W$. For example, one could add multiple examples of the same note played on different pianos to prevent from overemphasizing the characterisics of a specific instrument [cite FINDTHIS]. \citet{weninger2013discriminative} found including different spectral features for the onset, sustain and decay of each note to be useful. In these cases, note activations from different bases but which correspond to the same pitch are summed to form $88 \times N$ piano roll matrix.

@@

\subsubsection{Reported measures}
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 67.7\% & - \\ \hline
SVM with HMM & 70\% & 34.2 \\ \hline
Sup. NMF & - & - \\ \hline
AdaBoost & 75.2\% & - \\ \hline
\end{tabular}
\end{center}
% precision, recall, f
% 42.3, 68.8, .524

@@

Table \ref{table:ourevals} captures our evaluation of these methods. We expect these accuracy measures to be lower than they were reported in the original papers because we are using a smaller training dataset and not attempting to optimize the methods.

@@

Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 51.7\% & 84.7  \\ \hline
SVM with HMM & 62.7\% & 53.8  \\ \hline
Sup. NMF & 30.4\% & 92.4 \\ \hline
AdaBoost & 42.5\% & 113.9 \\ \hline

@@

We achieved the best accuracy with the SVM method with HMM smoothing from \citet{poliner2006discriminative}.

% Which method is fastest

% Which method has the best performance

% Which one is the simplest method

% Future directions

>>>>

\section{Terminology}

Semitones are the smallest music interval in Western music. On a piano, semitones are the adjacent keys.

@@

Some have suggested adding additional bases to $W$. For example, one could add multiple examples of the same note played on different pianos to prevent from overemphasizing the characterisics of a specific instrument. \citet{weninger2013discriminative} found including different spectral features for the onset, sustain and decay of each note to be useful. In these cases, note activations from different bases but which correspond to the same pitch are summed to form $88 \times N$ piano roll matrix.

@@

\subsubsection{Reported measures}
The table below reports the error measures from the original papers. $E_{tot}$, originally defined in \citet{poliner2006discriminative}, does not appear in all the papers, and the supervised NVM method only reports precision, recall, and f-score figures.

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 67.7\% & - \\ \hline
SVM with HMM & 70\% & 34.2 \\ \hline
Sup. NMF & 32.3\% & - \\ \hline
AdaBoost & 75.2\% & - \\ \hline
\end{tabular}
\end{center}
% precision, recall, f
% 42.3, 68.8, .524

@@

Table \ref{table:ourevals} captures our evaluation of these methods. We expect these accuracy measures to be lower than they were reported in the original papers because we are using a smaller training dataset and left the methods unoptimized.

@@

Algorithm & Accuracy & $E_{tot}$ \\ \hline
SVM & 51.7\% & 84.7  \\ \hline
SVM with HMM & 62.7\% & 53.8  \\ \hline
Sup. NMF & 30.8\% & 151.0 \\ \hline
AdaBoost & 42.5\% & 113.9 \\ \hline

@@

We achieved the best accuracy with the SVM method with HMM smoothing from \citet{poliner2006discriminative}. Across all methods, the raw output contained lots of spurious misclassifications, and smoothing was crucial for increasing accuracy, whether by hidden Markov models in the SVM method or median filtering with supervised NMF and AdaBoost. The AdaBoost method had suprisingly low accuracy relative to the other methods, although we spent the least amount of time optimizing this method.

We were surprised by the difficulties automated transcription presents. The ASDR envelope of piano notes complicates NMF retrieval of individual notes and results in duplicated notes. Cross-validating smoothing parameters was important for better accuracy. Aligning the spectrogram with ground truth data becomes nontrivial with the constant Q transform; unlike an FFT that has a definable center, the window size of the constant Q transform changes with each frequency.

% Which method is fastest
% Which method has the best performance
% Which one is the simplest method
% Future directions
